### 2025-02-27 paper-en.tex
Use script to scale figures
Rewrite citations

@@

% Отмасштабировать все картинки
\begin{figure}[!h]
    \centering
    \begin{picture}(150,170)
        \put(75,165){\thicklines{\circle*{5}}}
        \put(70,170){$c_1$}

        \put(35,35){\thicklines{\circle*{5}}}
        \put(30,20){$i_1$}

        \put(115,35){\thicklines{\circle*{5}}}
        \put(110,20){$i_2$}

        \bezier{300}(75,165)(10,100)(35,35)
        \put(5,100){$+1$}

        \bezier{300}(75,165)(56,100)(35,35)
        \put(56,80){$0$}

        \bezier{300}(75,165)(140,100)(115,35)
        \put(125,100){$-1$}

        \bezier{300}(75,165)(94,100)(115,35)
        \put(87,80){$0$}
    \end{picture}
    \caption{ Metagraph with edges weights of +1, 0, 0, -1. }
    \label{image:2}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(450,200)
        \put(75,165){\thicklines{\circle*{5}}}
        \put(70,170){$c_1$}
        \put(35,35){\thicklines{\circle*{5}}}
        \put(30,20){$i_1$}
        \put(115,35){\thicklines{\circle*{5}}}
        \put(110,20){$i_2$}

        \bezier{300}(75,165)(56,100)(35,35)
        \bezier{300}(75,165)(94,100)(115,35)
        \bezier{300}(75,165)(130,100)(135,35)
        \bezier{300}(175,165)(120,100)(115,35)

        \put(175,165){\thicklines{\circle*{5}}}
        \put(170,170){$c_1$}
        \put(135,35){\thicklines{\circle*{5}}}
        \put(130,20){$i_1$}
        \put(215,35){\thicklines{\circle*{5}}}
        \put(210,20){$i_2$}

        \bezier{300}(175,165)(156,100)(135,35)
        \bezier{300}(175,165)(194,100)(215,35)
        \bezier{300}(175,165)(230,100)(235,35)
        \bezier{300}(275,165)(220,100)(215,35)

        \put(275,165){\thicklines{\circle*{5}}}
        \put(270,170){$c_1$}
        \put(235,35){\thicklines{\circle*{5}}}
        \put(230,20){$i_1$}
        \put(315,35){\thicklines{\circle*{5}}}
        \put(310,20){$i_2$}

        \bezier{300}(275,165)(256,100)(235,35)
        \bezier{300}(275,165)(294,100)(315,35)
        \bezier{300}(275,165)(330,100)(335,35)
        \bezier{300}(375,165)(320,100)(315,35)

        \put(375,165){\thicklines{\circle*{5}}}
        \put(370,170){$c_1$}
        \put(335,35){\thicklines{\circle*{5}}}
        \put(330,20){$i_1$}
        \put(415,35){\thicklines{\circle*{5}}}
        \put(410,20){$i_2$}

        \bezier{300}(375,165)(356,100)(335,35)
        \bezier{300}(375,165)(394,100)(415,35)

        \bezier{700}(75,165)(245,100)(415,35)
        \bezier{700}(375,165)(205,100)(35,35)
    \end{picture}
    \caption{ 4-expansion of metagraph $G_1$. }
    \label{image:3}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(255,200)
        \put(0,165){$a.$}

        \put(35,165){\thicklines{\circle*{5}}}
        \put(30,170){$A$}
        \put(35,35){\thicklines{\circle*{5}}}
        \put(30,20){$B$}

        \bezier{300}(35,165)(10,100)(35,35)
        \put(0,100){$e_1$}
        \bezier{300}(35,165)(60,100)(35,35)
        \put(56,100){$e_ 2$}

        \put(110,165){$b.$}

        \put(145,165){\thicklines{\circle*{5}}}
        \put(140,170){$A^{(1)}$}
        \put(145,35){\thicklines{\circle*{5}}}
        \put(140,20){$B^{(1)}$}

        \thicklines
        \bezier{300}(145,165)(145,100)(145,35)
        \put(125,130){$e_0^{(1)}$}

        \bezier{300}(145,165)(165,100)(185,35)
        \put(147,85){$e_1^{(1)}$}
        \thinlines

        \put(185,165){\thicklines{\circle*{5}}}
        \put(180,170){$A^{(2)}$}
        \put(185,35){\thicklines{\circle*{5}}}
        \put(180,20){$B^{(2)}$}

        \bezier{300}(185,165)(185,100)(185,35)
        \put(165,130){$e_0^{(2)}$}

        \bezier{300}(185,165)(205,100)(225,35)
        \put(187,85){$e_1^{(2)}$}

        \put(225,165){\thicklines{\circle*{5}}}
        \put(220,170){$A^{(3)}$}
        \put(225,35){\thicklines{\circle*{5}}}
        \put(220,20){$B^{(3)}$}

        \bezier{300}(225,165)(225,100)(225,35)
        \put(205,130){$e_0^{(3)}$}

        \bezier{300}(225,165)(232,50)(145,35)
        \put(190,45){$e_1^{(3)}$}
    \end{picture}
    \caption{ a. Metagraph. b. 3-expansion of metagraph. }
    \label{metagraph_3_expansion}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(150,200)
        \put(75,165){\thicklines{\circle*{5}}}
        \put(70,170){$v_1$}

        \put(35,35){\thicklines{\circle*{5}}}
        \put(30,20){$v_2$}

        \put(115,35){\thicklines{\circle*{5}}}
        \put(110,20){$v_3$}

        \bezier{300}(75,165)(10,100)(35,35)
        \put(5,100){$w_1$}

        \bezier{300}(75,165)(56,100)(35,35)
        \put(56,80){$w_2$}

        \bezier{300}(75,165)(140,100)(115,35)
        \put(125,100){$w_3$}

        \bezier{300}(75,165)(94,100)(115,35)
        \put(87,80){$w_4$}
    \end{picture}
    \caption{ Metagraph $G$, with variable weights of edges $w_1, w_2, w_3, w_4$. }
    \label{neq_system_graph}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(380,200)
        \put(50,165){\thicklines{\circle*{5}}}
        \put(35,35){\thicklines{\circle*{5}}}
        \put(65,35){\thicklines{\circle*{5}}}

        \bezier{300}(50,165)(42,100)(35,35)
        \bezier{300}(50,165)(57,100)(65,35)

        \put(120,165){\thicklines{\circle*{5}}}
        \put(105,35){\thicklines{\circle*{5}}}
        \put(135,35){\thicklines{\circle*{5}}}

        \bezier{300}(120,165)(127,100)(135,35)
        \bezier{300}(120,165)(197,100)(275,35)

        \put(190,165){\thicklines{\circle*{5}}}
        \put(175,35){\thicklines{\circle*{5}}}
        \put(205,35){\thicklines{\circle*{5}}}

        \bezier{300}(190,165)(217,100)(245,35)
        \bezier{300}(190,165)(267,100)(345,35)

        \put(260,165){\thicklines{\circle*{5}}}
        \put(245,35){\thicklines{\circle*{5}}}
        \put(275,35){\thicklines{\circle*{5}}}

        \bezier{300}(260,165)(252,100)(245,35)
        \bezier{300}(260,165)(267,100)(275,35)
        \bezier{300}(260,165)(287,100)(315,35)
        \bezier{600}(260,165)(172,50)(65,35)

        \put(330,165){\thicklines{\circle*{5}}}
        \put(315,35){\thicklines{\circle*{5}}}
        \put(345,35){\thicklines{\circle*{5}}}

        \bezier{300}(330,165)(322,100)(315,35)
        \bezier{300}(330,165)(337,100)(345,35)
        \bezier{600}(330,165)(182,150)(35,35)
        \bezier{600}(330,165)(242,50)(135,35)

        \thicklines
        \bezier{300}(50,165)(77,100)(105,35)
        \bezier{300}(120,165)(112,100)(105,35)
        \bezier{300}(120,165)(147,100)(175,35)
        \bezier{300}(190,165)(182,100)(175,35)
        \bezier{300}(190,165)(197,100)(205,35)
        \bezier{300}(50,165)(127,100)(205,35)
    \end{picture}
    \caption{ Expansion of a metagraph with weights obtained as a solution of the system \eqref{eqs:cycle_search_neqs}. }
    \label{neq_system_res}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(300,200)
        \put(65,165){\thicklines{\circle*{5}}}
        \put(155,165){\thicklines{\circle*{5}}}
        \put(245,165){\thicklines{\circle*{5}}}

        \put(35,35){\thicklines{\circle*{5}}}
        \put(65,35){\thicklines{\circle*{5}}}
        \put(95,35){\thicklines{\circle*{5}}}

        \bezier{500}(35,35)(35,35)(65,165)
        \bezier{500}(65,35)(65,35)(65,165)
        \bezier{500}(95,35)(95,35)(65,165)
        \bezier{500}(35,35)(35,35)(155,165)
        \bezier{500}(65,35)(65,35)(155,165)
        \bezier{500}(95,35)(95,35)(155,165)
        \bezier{500}(35,35)(35,35)(245,165)
        \bezier{500}(65,35)(65,35)(245,165)
        \bezier{500}(95,35)(95,35)(245,165)

        \put(125,35){\thicklines{\circle*{5}}}
        \put(155,35){\thicklines{\circle*{5}}}
        \put(185,35){\thicklines{\circle*{5}}}

        \bezier{500}(125,35)(125,35)(65,165)
        \bezier{500}(155,35)(155,35)(65,165)
        \bezier{500}(185,35)(185,35)(65,165)
        \bezier{500}(125,35)(125,35)(155,165)
        \bezier{500}(155,35)(155,35)(155,165)
        \bezier{500}(185,35)(185,35)(155,165)
        \bezier{500}(125,35)(125,35)(245,165)
        \bezier{500}(155,35)(155,35)(245,165)
        \bezier{500}(185,35)(185,35)(245,165)

        \put(215,35){\thicklines{\circle*{5}}}
        \put(245,35){\thicklines{\circle*{5}}}
        \put(275,35){\thicklines{\circle*{5}}}

        \bezier{500}(215,35)(215,35)(65,165)
        \bezier{500}(245,35)(245,35)(65,165)
        \bezier{500}(275,35)(275,35)(65,165)
        \bezier{500}(215,35)(215,35)(155,165)
        \bezier{500}(245,35)(245,35)(155,165)
        \bezier{500}(275,35)(275,35)(155,165)
        \bezier{500}(215,35)(215,35)(245,165)
        \bezier{500}(245,35)(245,35)(245,165)
        \bezier{500}(275,35)(275,35)(245,165)
    \end{picture}
    \caption{ Complete bipartite graph with parts consisting of 3 and 9 vertices. }
    \label{full_graph_3_by_9}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(200,200)
        \put(65,165){\thicklines{\circle*{5}}}
        \put(155,165){\thicklines{\circle*{5}}}

        \put(35,35){\thicklines{\circle*{5}}}
        \put(110,35){\thicklines{\circle*{5}}}
        \put(185,35){\thicklines{\circle*{5}}}

        \bezier{500}(35,35)(35,35)(65,165)
        \put(40,140){$e_1$}
        \bezier{500}(110,35)(110,35)(65,165)
        \put(65,120){$e_2$}
        \bezier{500}(185,35)(185,35)(65,165)
        \put(85,150){$e_3$}

        \bezier{500}(35,35)(35,35)(155,165)
        \put(125,150){$e_4$}
        \bezier{500}(110,35)(110,35)(155,165)
        \put(145,120){$e_5$}
        \bezier{500}(185,35)(185,35)(155,165)
        \put(165,140){$e_6$}
    \end{picture}
    \caption{ Complete metagraph $G$ with parts consisting of 2 and 3 vertices. }
    \label{full_graph_2_by_3}
\end{figure}

@@

% 2
\bibitem{johnson}
S.\,J. Johnson,
Introducing Low-Density Parity-Check Codes.
~-- University of Newcastle, Australia, 2006.

% 3
\bibitem{gallager}
R.\,G. Gallager,
Low-density parity-check codes
~-- IRE Transactions on Information Theory, 1962.

@@

% 6
\bibitem{tutte_graph_definition}
W.T. Tutte, Graph Theory
~-- % https://books.google.rs/books?id=uTGhooU37h4C&printsec=frontcover#v=onepage&q&f=false
Chapter 1, page 1

% 7
\bibitem{margulis_construction}
G. A. MARGULIS EXPLICIT CONSTRUCTIONS OF GRAPHS WITHOUT SHORT CYCLES AND LOW DENSITY CODES 
%% https://sci-hub.se/10.1007/bf02579283

% 9
%% Критика метода Маргулиса
\bibitem{margulis_critique}
David J.C. MacKay, Michael S. Postol, Weaknesses of Margulis and Ramanujan–Margulis Low-Density Parity-Check Codes
% https://www.inference.org.uk/mackay/margulis.pdf

% 8
\bibitem{imrich_construction}
Imrich, W. (1984). Explicit construction of regular graphs without small cycles
%% https://sci-hub.se/10.1007/bf02579157

% 10
\bibitem{ldpc_encoding}
T. J. Richardson and R. L. Urbanke, “Efficient encoding of low-density parity-check codes”, IEEE Transactions on Information Theory 47, 638 (2001)

% 11
\bibitem{algebraic_aproach_to_sc_ldpc}
A. Beemer, S. Habib, C. A. Kelley, and J. Kliewer, “A Generalized Algebraic Approach to Optimizing SC-LDPC Codes”. (2017)
% https://web.njit.edu/~jkliewer/wp/paper/BHKK_Allerton17.pdf

% 12
\bibitem{lifts_of_graphs}
C. A. Kelley, “On codes designed via algebraic lifts of graphs,”
% https://typeset.io/pdf/on-codes-designed-via-algebraic-lifts-of-graphs-34h5sq5koc.pdf

% 13
\bibitem{vasic_combinatorial_construction}
B. Vasic, Combinatorial Constructions of Low-Density Parity-Check Codes for Iterative Decoding
% https://repository.arizona.edu/bitstream/handle/10150/641965/Combinatorial%20Constructions%20of%20Low-DensityParity-Check%20Codes%20for%20Iterative%20Decoding.pdf;jsessionid=9F016719B821C7D7CEBB9C48D7B37CB1?sequence=1

%14
\bibitem{Kim2002ExplicitCO}
Jon-Lark Kim, Uri N. Peled. Irina G. Perepelitsa. Vera Pless, Explicit Construction of Families of LDPC Codes with Girth at Least Six, 2002
%https://homepages.math.uic.edu/~pless/preprint/allerton.pdf

>>>>

% Abstract 250 слов

@@

% Отмасштабировать все картинки
\begin{figure}[!h]
    \centering
    \begin{picture}(100,110)
        \put(51,101){\thicklines{\circle*{5}}}
        \put(48,105){$c_1$}

        \put(25,15){\thicklines{\circle*{5}}}
        \put(21,5){$i_1$}

        \put(78,15){\thicklines{\circle*{5}}}
        \put(75,5){$i_2$}

        \bezier{300}(51,101)(8,58)(25,15)
        \put(5,58){$+1$}

        \bezier{300}(51,101)(39,58)(25,15)
        \put(39,45){$0$}

        \bezier{300}(51,101)(95,58)(78,15)
        \put(85,58){$-1$}

        \bezier{300}(51,101)(64,58)(78,15)
        \put(59,45){$0$}
    \end{picture}
    \caption{ Metagraph with edges weights of +1, 0, 0, -1. }
    \label{image:2}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(266,110)
        \put(35,101){\thicklines{\circle*{5}}}
        \put(31,105){$c_1$}
        \put(8,15){\thicklines{\circle*{5}}}
        \put(5,5){$i_1$}
        \put(61,15){\thicklines{\circle*{5}}}
        \put(58,5){$i_2$}

        \bezier{300}(35,101)(22,58)(8,15)
        \bezier{300}(35,101)(47,58)(61,15)
        \bezier{300}(35,101)(71,58)(75,15)
        \bezier{300}(101,101)(65,58)(61,15)

        \put(101,101){\thicklines{\circle*{5}}}
        \put(98,105){$c_1$}
        \put(75,15){\thicklines{\circle*{5}}}
        \put(71,5){$i_1$}
        \put(128,15){\thicklines{\circle*{5}}}
        \put(125,5){$i_2$}

        \bezier{300}(101,101)(89,58)(75,15)
        \bezier{300}(101,101)(114,58)(128,15)
        \bezier{300}(101,101)(138,58)(141,15)
        \bezier{300}(168,101)(131,58)(128,15)

        \put(168,101){\thicklines{\circle*{5}}}
        \put(165,105){$c_1$}
        \put(141,15){\thicklines{\circle*{5}}}
        \put(138,5){$i_1$}
        \put(195,15){\thicklines{\circle*{5}}}
        \put(191,5){$i_2$}

        \bezier{300}(168,101)(155,58)(141,15)
        \bezier{300}(168,101)(181,58)(195,15)
        \bezier{300}(168,101)(205,58)(208,15)
        \bezier{300}(235,101)(198,58)(195,15)

        \put(235,101){\thicklines{\circle*{5}}}
        \put(231,105){$c_1$}
        \put(208,15){\thicklines{\circle*{5}}}
        \put(205,5){$i_1$}
        \put(261,15){\thicklines{\circle*{5}}}
        \put(258,5){$i_2$}

        \bezier{300}(235,101)(222,58)(208,15)
        \bezier{300}(235,101)(247,58)(261,15)

        \bezier{700}(35,101)(148,58)(261,15)
        \bezier{700}(235,101)(121,58)(8,15)
    \end{picture}
    \caption{ 4-expansion of metagraph $G_1$. }
    \label{image:3}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(164,110)
        \put(5,101){$a.$}

        \put(28,101){\thicklines{\circle*{5}}}
        \put(25,105){$A$}
        \put(28,15){\thicklines{\circle*{5}}}
        \put(25,5){$B$}

        \bezier{300}(28,101)(11,58)(28,15)
        \put(5,58){$e_1$}
        \bezier{300}(28,101)(45,58)(28,15)
        \put(42,58){$e_ 2$}

        \put(78,101){$b.$}

        \put(101,101){\thicklines{\circle*{5}}}
        \put(98,105){$A^{(1)}$}
        \put(101,15){\thicklines{\circle*{5}}}
        \put(98,5){$B^{(1)}$}

        \thicklines
        \bezier{300}(101,101)(101,58)(101,15)
        \put(88,78){$e_0^{(1)}$}

        \bezier{300}(101,101)(115,58)(128,15)
        \put(103,48){$e_1^{(1)}$}
        \thinlines

        \put(128,101){\thicklines{\circle*{5}}}
        \put(125,105){$A^{(2)}$}
        \put(128,15){\thicklines{\circle*{5}}}
        \put(125,5){$B^{(2)}$}

        \bezier{300}(128,101)(128,58)(128,15)
        \put(115,78){$e_0^{(2)}$}

        \bezier{300}(128,101)(141,58)(155,15)
        \put(129,48){$e_1^{(2)}$}

        \put(155,101){\thicklines{\circle*{5}}}
        \put(151,105){$A^{(3)}$}
        \put(155,15){\thicklines{\circle*{5}}}
        \put(151,5){$B^{(3)}$}

        \bezier{300}(155,101)(155,58)(155,15)
        \put(141,78){$e_0^{(3)}$}

        \bezier{300}(155,101)(159,25)(101,15)
        \put(131,21){$e_1^{(3)}$}
    \end{picture}
    \caption{ a. Metagraph. b. 3-expansion of metagraph. }
    \label{metagraph_3_expansion}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(100,110)
        \put(51,101){\thicklines{\circle*{5}}}
        \put(48,105){$v_1$}

        \put(25,15){\thicklines{\circle*{5}}}
        \put(21,5){$v_2$}

        \put(78,15){\thicklines{\circle*{5}}}
        \put(75,5){$v_3$}

        \bezier{300}(51,101)(8,58)(25,15)
        \put(5,58){$w_1$}

        \bezier{300}(51,101)(39,58)(25,15)
        \put(39,45){$w_2$}

        \bezier{300}(51,101)(95,58)(78,15)
        \put(85,58){$w_3$}

        \bezier{300}(51,101)(64,58)(78,15)
        \put(59,45){$w_4$}
    \end{picture}
    \caption{ Metagraph $G$, with variable weights of edges $w_1, w_2, w_3, w_4$. }
    \label{neq_system_graph}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(248,110)
        \put(16,105){\thicklines{\circle*{5}}}
        \put(5,5){\thicklines{\circle*{5}}}
        \put(28,5){\thicklines{\circle*{5}}}

        \bezier{300}(16,105)(10,55)(5,5)
        \bezier{300}(16,105)(21,55)(28,5)

        \put(70,105){\thicklines{\circle*{5}}}
        \put(58,5){\thicklines{\circle*{5}}}
        \put(81,5){\thicklines{\circle*{5}}}

        \bezier{300}(70,105)(75,55)(81,5)
        \bezier{300}(70,105)(129,55)(189,5)

        \put(124,105){\thicklines{\circle*{5}}}
        \put(112,5){\thicklines{\circle*{5}}}
        \put(135,5){\thicklines{\circle*{5}}}

        \bezier{300}(124,105)(145,55)(166,5)
        \bezier{300}(124,105)(183,55)(243,5)

        \put(178,105){\thicklines{\circle*{5}}}
        \put(166,5){\thicklines{\circle*{5}}}
        \put(189,5){\thicklines{\circle*{5}}}

        \bezier{300}(178,105)(171,55)(166,5)
        \bezier{300}(178,105)(183,55)(189,5)
        \bezier{300}(178,105)(198,55)(220,5)
        \bezier{600}(178,105)(110,16)(28,5)

        \put(231,105){\thicklines{\circle*{5}}}
        \put(220,5){\thicklines{\circle*{5}}}
        \put(243,5){\thicklines{\circle*{5}}}

        \bezier{300}(231,105)(225,55)(220,5)
        \bezier{300}(231,105)(237,55)(243,5)
        \bezier{600}(231,105)(118,93)(5,5)
        \bezier{600}(231,105)(164,16)(81,5)

        \thicklines
        \bezier{300}(16,105)(37,55)(58,5)
        \bezier{300}(70,105)(64,55)(58,5)
        \bezier{300}(70,105)(91,55)(112,5)
        \bezier{300}(124,105)(118,55)(112,5)
        \bezier{300}(124,105)(129,55)(135,5)
        \bezier{300}(16,105)(75,55)(135,5)
    \end{picture}
    \caption{ Expansion of a metagraph with weights obtained as a solution of the system \eqref{eqs:cycle_search_neqs}. }
    \label{neq_system_res}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(194,110)
        \put(28,105){\thicklines{\circle*{5}}}
        \put(97,105){\thicklines{\circle*{5}}}
        \put(166,105){\thicklines{\circle*{5}}}

        \put(5,5){\thicklines{\circle*{5}}}
        \put(28,5){\thicklines{\circle*{5}}}
        \put(51,5){\thicklines{\circle*{5}}}

        \bezier{500}(5,5)(5,5)(28,105)
        \bezier{500}(28,5)(28,5)(28,105)
        \bezier{500}(51,5)(51,5)(28,105)
        \bezier{500}(5,5)(5,5)(97,105)
        \bezier{500}(28,5)(28,5)(97,105)
        \bezier{500}(51,5)(51,5)(97,105)
        \bezier{500}(5,5)(5,5)(166,105)
        \bezier{500}(28,5)(28,5)(166,105)
        \bezier{500}(51,5)(51,5)(166,105)

        \put(74,5){\thicklines{\circle*{5}}}
        \put(97,5){\thicklines{\circle*{5}}}
        \put(120,5){\thicklines{\circle*{5}}}

        \bezier{500}(74,5)(74,5)(28,105)
        \bezier{500}(97,5)(97,5)(28,105)
        \bezier{500}(120,5)(120,5)(28,105)
        \bezier{500}(74,5)(74,5)(97,105)
        \bezier{500}(97,5)(97,5)(97,105)
        \bezier{500}(120,5)(120,5)(97,105)
        \bezier{500}(74,5)(74,5)(166,105)
        \bezier{500}(97,5)(97,5)(166,105)
        \bezier{500}(120,5)(120,5)(166,105)

        \put(143,5){\thicklines{\circle*{5}}}
        \put(166,5){\thicklines{\circle*{5}}}
        \put(189,5){\thicklines{\circle*{5}}}

        \bezier{500}(143,5)(143,5)(28,105)
        \bezier{500}(166,5)(166,5)(28,105)
        \bezier{500}(189,5)(189,5)(28,105)
        \bezier{500}(143,5)(143,5)(97,105)
        \bezier{500}(166,5)(166,5)(97,105)
        \bezier{500}(189,5)(189,5)(97,105)
        \bezier{500}(143,5)(143,5)(166,105)
        \bezier{500}(166,5)(166,5)(166,105)
        \bezier{500}(189,5)(189,5)(166,105)
    \end{picture}
    \caption{ Complete bipartite graph with parts consisting of 3 and 9 vertices. }
    \label{full_graph_3_by_9}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{picture}(125,110)
        \put(28,105){\thicklines{\circle*{5}}}
        \put(97,105){\thicklines{\circle*{5}}}

        \put(5,5){\thicklines{\circle*{5}}}
        \put(62,5){\thicklines{\circle*{5}}}
        \put(120,5){\thicklines{\circle*{5}}}

        \bezier{500}(5,5)(5,5)(28,105)
        \put(8,85){$e_1$}
        \bezier{500}(62,5)(62,5)(28,105)
        \put(28,70){$e_2$}
        \bezier{500}(120,5)(120,5)(28,105)
        \put(43,93){$e_3$}

        \bezier{500}(5,5)(5,5)(97,105)
        \put(74,93){$e_4$}
        \bezier{500}(62,5)(62,5)(97,105)
        \put(89,70){$e_5$}
        \bezier{500}(120,5)(120,5)(97,105)
        \put(105,85){$e_6$}
    \end{picture}
    \caption{ Complete metagraph $G$ with parts consisting of 2 and 3 vertices. }
    \label{full_graph_2_by_3}
\end{figure}

@@

% 2
\bibitem{johnson}
Johnson, Sarah. (2008). Introducing Low-Density Parity-Check Codes. 
% ~-- University of Newcastle, Australia, 2006.

% 3
\bibitem{gallager}
R. Gallager, "Low-density parity-check codes," in IRE Transactions on Information Theory, vol. 8, no. 1, pp. 21-28, January 1962, doi: 10.1109/TIT.1962.1057683

@@

% 6
\bibitem{tutte_graph_definition}
W.T. Tutte, Graph Theory. Cambridge University Press, Cambridge, 2001, 360 pp.
% https://books.google.rs/books?id=uTGhooU37h4C&printsec=frontcover#v=onepage&q&f=false

% 7
\bibitem{margulis_construction}
Margulis, G. A. (1982). Explicit constructions of graphs without short cycles and low density codes. Combinatorica, 2(1), 71–78. 
doi:10.1007/bf02579283
%% https://sci-hub.se/10.1007/bf02579283

% 9
%% Критика метода Маргулиса
\bibitem{margulis_critique}
David J.C. MacKay, Michael S. Postol, Weaknesses of Margulis and Ramanujan-Margulis Low-Density Parity-Check Codes, Electronic Notes in Theoretical Computer Science, Volume 74, 2003, Pages 97-104, ISSN 1571-0661, doi:10.1016/S1571-0661(04)80768-0.
% https://www.inference.org.uk/mackay/margulis.pdf

% 8
\bibitem{imrich_construction}
Imrich, W. (1984). Explicit construction of regular graphs without small cycles. Combinatorica, 4(1), 53–59. doi:10.1007/bf02579157 
%% https://sci-hub.se/10.1007/bf02579157

% 10
\bibitem{ldpc_encoding}
T. J. Richardson and R. L. Urbanke, "Efficient encoding of low-density parity-check codes," in IEEE Transactions on Information Theory, vol. 47, no. 2, pp. 638-656, Feb 2001, doi: 10.1109/18.910579

% 11
\bibitem{algebraic_aproach_to_sc_ldpc}
Beemer, A., Habib, S., Kelley, C. A., & Kliewer, J. (2017). A generalized algebraic approach to optimizing SC-LDPC codes. In 55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017 (pp. 672-679). (55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017; Vol. 2018-January). Institute of Electrical and Electronics Engineers Inc. doi:10.1109/ALLERTON.2017.8262802

% https://web.njit.edu/~jkliewer/wp/paper/BHKK_Allerton17.pdf

% 12
\bibitem{lifts_of_graphs}
C. A. Kelley, "On codes designed via algebraic lifts of graphs," 2008 46th Annual Allerton Conference on Communication, Control, and Computing, Monticello, IL, USA, 2008, pp. 1254-1261, doi: 10.1109/ALLERTON.2008.4797704.

% https://typeset.io/pdf/on-codes-designed-via-algebraic-lifts-of-graphs-34h5sq5koc.pdf

% 13
\bibitem{vasic_combinatorial_construction}
B. Vasic and O. Milenkovic, "Combinatorial constructions of low-density parity-check codes for iterative decoding," in IEEE Transactions on Information Theory, vol. 50, no. 6, pp. 1156-1176, June 2004, doi: 10.1109/TIT.2004.828066.
% https://repository.arizona.edu/bitstream/handle/10150/641965/Combinatorial%20Constructions%20of%20Low-DensityParity-Check%20Codes%20for%20Iterative%20Decoding.pdf;jsessionid=9F016719B821C7D7CEBB9C48D7B37CB1?sequence=1

%14
\bibitem{Kim2002ExplicitCO}
Kim, Jon-Lark, Uri N. Peled, Irina G. Perepelitsa and Vera Pless. “Explicit Construction of Families of LDPC Codes with Girth at Least Six.” (2002).

%https://homepages.math.uic.edu/~pless/preprint/allerton.pdf
